---
title: "Analysis of the recognition task of the ANTiEM experiment."
output: html_document
---

Author: Javier Ortiz-Tudela (Goethe Uni)

Started on: 11.11.22

We will look at retrieval performance as a function of the encoding conditions. At this stage I'm only computing averages and creating some plots for visualisation. It doesn't make sense to run stats with only five participants.

```{r setup, include=FALSE}
## Load libraries.
library(ggpubr)
library(rstatix)
library(dplyr)

## Set directories
main_dir <- '/Users/javierortiz/Library/CloudStorage/GoogleDrive-fjavierot@gmail.com/Mi unidad/colab_projects/Memory_Attention_Javi_Fer/'
data_dir <- paste(main_dir , "pilot_data/", sep="/")
func_dir <- '/Users/javierortiz/github_repos/antiem/code/_functions'
fig_dir <- '/Users/javierortiz/Library/CloudStorage/GoogleDrive-fjavierot@gmail.com/Mi unidad/colab_projects/Memory_Attention_Javi_Fer/figures'

```

```{r load data, include=FALSE}
# File name 
filename <- 'group_task-antiem_beh.csv'

 # Read data
full_data <- read.csv2(paste(data_dir,  filename, sep="/"), sep=",")

# Fix some R stuff
full_data$anti_rt <- as.numeric(full_data$anti_rt)
full_data$recog_rt <- as.numeric(full_data$recog_rt)
full_data$old_or_new <- as.factor(full_data$old_or_new)

# Select only new trials
full_data <- full_data %>% 
  filter(old_or_new == 1)

# Select only correct encoding trials
full_data <- full_data %>%
  filter(anti_acc == 1)
```
# Congruency
We can aggregate by congruity to look at performance.

```{r}
# Aggregate
agg_data <- full_data %>% 
  group_by(participant, congruency) %>%
  summarise(mean_acc = mean(recog_acc),
            sd_acc = sd(recog_acc))

# Plot
ggplot(data = agg_data,
       aes(x = congruency, y = mean_acc, fill = congruency)) +
  geom_boxplot(position = position_nudge(x = 0, y = 0), alpha = .4)+
  geom_point(size = 1, alpha = 0.3) +
  geom_line(aes(group = participant), alpha = .3) +
  stat_summary(fun= mean, geom="point", shape=20, size=7, color="red", fill="red") +
  ggtitle("Mean acc by congruity") +
  ylim(c(0,1)) +
  ylab("Recog acc") +
  labs(fill='Control') +
  theme(plot.title.position = "plot") +
  theme_bw()

full_data %>% 
  group_by(congruency) %>% 
  summarise(cong_acc = mean(recog_acc))
```

# Validity
We can aggregate by validity to look at performance.
```{r}
# Aggregate
agg_data <- full_data %>% 
  group_by(participant, validity) %>% 
  summarise(mean_acc = mean(recog_acc),
            sd_acc = sd(recog_acc))

# Plot
ggplot(data = agg_data,
       aes(x = validity, y = mean_acc, fill = validity)) +
  geom_boxplot(position = position_nudge(x = 0, y = 0), alpha = .4)+
  geom_point(size = 1, alpha = 0.3) +
  geom_line(aes(group = participant), alpha = .3) +
  stat_summary(fun= mean, geom="point", shape=20, size=7, color="red", fill="red") +
  ggtitle("Mean acc by validity") +
  ylim(c(0,1)) +
  ylab("Recog acc") +
  labs(fill='Orienting') +
  theme(plot.title.position = "plot") +
  theme_bw()

full_data %>% 
  group_by(validity) %>% 
  summarise(val_acc = mean(recog_acc))

```
# Tone
We can aggregate by tone to look at performance.
```{r}
# Aggregate
agg_data <- full_data %>% 
  group_by(participant, tone) %>% 
  summarise(mean_acc = mean(recog_acc),
            sd_acc = sd(recog_acc)) %>% 
  ungroup()

# Plot
ggplot(data = agg_data,
       aes(x = tone, y = mean_acc, fill = tone)) +
  geom_boxplot(position = position_nudge(x = 0, y = 0), alpha = .4)+
  geom_point(size = 1, alpha = 0.3) +
  geom_line(aes(group = participant), alpha = .3) +
  stat_summary(fun= mean, geom="point", shape=20, size=7, color="red", fill="red") +
  ggtitle("Mean acc by tone") +
  ylim(c(0,1)) +
  ylab("Recog acc") +
  labs(fill='Alertness') +
  theme(plot.title.position = "plot") +
  theme_bw()

full_data %>% 
  group_by(tone) %>% 
  summarise(alert_acc = mean(recog_acc))

```

## Compute rANOVA
This is just an example that we can re-use to compute rANOVAs when it becomes necessary
```{r}
# Need to select only the to-be-used columns
data_to_stat <-  subset(x = agg_data, select = c(participant, tone, mean_acc))

# Run ANOVA
res.aov <- anova_test(data = data_to_stat, dv = mean_acc, wid = participant, within = c(tone))
get_anova_table(res.aov)

# Pair-wise comparisons
pwc <- data_to_stat %>%
  pairwise_t_test(
    mean_acc ~ tone, paired = TRUE,
    p.adjust.method = "bonferroni"
  )
pwc

```

